Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-28 Master Thesis/synopsis.tex
Formulation

If $K'/K$ is henselian with respect to an extension $w$ of $v$, then there exists a uniquely determined $K$-embedding $K_v\to K'$, so that $w$ extends $\overline{v}$.

@@

\begin{lemma}\label{2.2}
Let $K$ be henselian with respect to two different valuations $w_1,w_2\in |\operatorname{Spv}(K)|$. Then the following statements are equivalent: 
\begin{enumerate}[(i)]
\item $K$ is not algebraically closed.
\item $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K),\ v(w_1)=v(w_2)$ and $k(v(w_1))$ is separably closed
\end{enumerate}
In this case, we have $\operatorname{cd}(G_K)\leq 2$.
\end{lemma}

\begin{proof}
\begin{itemize}
\item Assume that $K$ is not algebraically closed. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we can see that $w_1,w_2$ are not of rank $1$. Thus they are of rank $2$ and by Lemma \ref{rank-dimension-inequality} we can see $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$. Set $v_i=v(w_i)\in\operatorname{Spv}^{(1)}_\text{rd}(K)$. By Lemma \ref{2.2-pre} $K$ is henselian with respect to both $v_1$ and $v_2$. Again, by the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, $v_1 = v_2$. Furthermore $k(v_1) = k(v_2)$ is henselian with respect to two different valuations of rank $1$, namely $w_1\mod v_1$ and $w_2\mod v_1$, making $k(v_1)$ separably closed.
\item Now assume (ii) holds.
\item The second assertion follows from the first and from [K2], §5, Theorem 1.\qedhere
\end{itemize}
\end{proof}

>>>>

\textit{If $K'/K$ is henselian with respect to an extension $w$ of $v$, then there exists a uniquely determined $K$-embedding $K_v\to K'$, so that $w$ extends $\overline{v}$.}

@@

\begin{lemma}\label{2.2}
Let $K$ be henselian with respect to two different valuations $w_1,w_2\in |\operatorname{Spv}(K)|$. Then the following statements are equivalent: 
\begin{enumerate}[(i)]
\item $K$ is not algebraically closed.
\item $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K),\ v(w_1)=v(w_2)$ and $k(v(w_1))$ is separably closed.
\end{enumerate}
In this case, we have $\operatorname{cd}(G_K)\leq 2$.
\end{lemma}

\begin{proof}
\begin{itemize}
\item Assume that $K$ is not algebraically closed. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we can see that $w_1,w_2$ are not of rank $1$. Thus they are of rank $2$ and by Lemma \ref{rank-dimension-inequality} we can see $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$. Set $v_i=v(w_i)\in\operatorname{Spv}^{(1)}_\text{rd}(K)$. By Lemma \ref{2.2-pre} $K$ is henselian with respect to both $v_1$ and $v_2$. Again, by the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we get $v_1 = v_2$. Furthermore $k(v_1) = k(v_2)$ is henselian with respect to two different valuations of rank $1$, namely $w_1\mod v_1$ and $w_2\mod v_1$, making $k(v_1)$ separably closed.
\item Now assume (ii) holds.
\item The second assertion follows from the first and from [K2], §5, Theorem 1.\qedhere
\end{itemize}
\end{proof}
